Real-time resolution of short-read assembly graph using ONT long reads

### 2020-11-22 paper_edit.tex

\begin{table}[!hpt]
\begin{adjustwidth}{-2.25in}{0in}
\centering
\caption[Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized SPAdes output]{Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized \spades{} output. Circular contigs are highlighted in \textbf{bold}, fragmented assemblies are presented as X$\vert$Y where X is the total length and Y is the number of supposed contigs making up X.}
\label{tab:npgraph_real}
\begin{tabular}{p{4cm}|r|r|l}
 & \unicycler{} & \npgraph{} & Replicons (based on $\mathtt{PlasmidFinder}$ 1.3) \\ \thickhline
\emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
CAV1374 & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
 & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\
 & \textbf{85,575} & \textbf{85,575} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
 & \textbf{43,621} & \textbf{43,621} & repA\_1\_pKPC-2\_CP013325 \\
 & \textbf{3,223} & \textbf{3,223} & - \\
 & \textbf{1,916} & \textbf{1,916} & ColRNAI\_1\_\_DQ298019 \\
 & 14,464$\vert$3 & 14,456$\vert$2 & - \\ \hline
\emph{Enterobacter cloacae} & 4,806,666$\vert$2 & 4,858,438$\vert$2 & Chromosome \\
CAV1411 & \textbf{90,451} & 90,693$\vert$2 & IncR\_1\_\_DQ449578 \\
 & \textbf{33,610} & \textbf{33,610} & repA\_1\_pKPC-2\_CP013325 \\
 & 13,129$\vert$2 & 14,542$\vert$4 & - \\ \hline
\emph{Klebsiella oxytoca}  & 6,153,947$\vert$5 & \textbf{6,155,762} & Chromosome \\
CAV1015 & \textbf{113,105} & \textbf{113,105} & \begin{tabular}[c]{@{}l@{}}IncFII(SARC14)\_1\_SARC14\_JQ418540;\\ IncFII(S)\_1\_\_CP000858\end{tabular} \\
 & \textbf{111,395} & \textbf{111,395} & - \\
 & \textbf{108,418} & 109,209$\vert$13 & IncFIB(K)\_1\_Kpn3\_JN233704 \\
 & \textbf{76,183} & \textbf{76,186} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
 & \textbf{11,638} & 11,892$\vert$2 & - \\ \hline
\end{tabular}
\end{adjustwidth}
\end{table}

>>>>

\begin{table}[!hpt]
\begin{adjustwidth}{-2.25in}{0in}
\centering
\caption[Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized SPAdes output]{Assembly of real data sets using \unicycler{} and \npgraph{} with the optimized \spades{} output. Circular contigs are highlighted in \textbf{bold}, fragmented assemblies are presented as X$\vert$Y where X is the total length and Y is the number of supposed contigs making up X.}
\label{tab:npgraph_real}
\begin{tabular}{p{4cm}|r|r|l}
 & \unicycler{} & \npgraph{} & Replicons (based on $\mathtt{PlasmidFinder}$ 1.3) \\ \thickhline
\emph{Citrobacter freundii} & \textbf{5,029,534} & \textbf{5,029,486} & Chromosome \\
CAV\review{1741} & \textbf{109688} & \textbf{109688} & IncFIB(pHCM2)\_1\_pHCM2\_AL513384 \\
 & \textbf{100,873} & \textbf{100,873} & IncFIB(pB171)\_1\_pB171\_AB024946 \\
 & \textbf{85,575} & \textbf{85,575} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
 & \textbf{43,621} & \textbf{43,621} & repA\_1\_pKPC-2\_CP013325 \\
 & \textbf{3,223} & \textbf{3,223} & - \\
 & \textbf{1,916} & \textbf{1,916} & ColRNAI\_1\_\_DQ298019 \\
 & 14,464$\vert$3 & 14,456$\vert$2 & - \\ \hline
\emph{Enterobacter cloacae} & 4,806,666$\vert$2 & 4,858,438$\vert$2 & Chromosome \\
CAV1411 & \textbf{90,451} & 90,693$\vert$2 & IncR\_1\_\_DQ449578 \\
 & \textbf{33,610} & \textbf{33,610} & repA\_1\_pKPC-2\_CP013325 \\
 & 13,129$\vert$2 & 14,542$\vert$4 & - \\ \hline
\emph{Klebsiella oxytoca}  & 6,153,947$\vert$5 & \textbf{6,155,762} & Chromosome \\
CAV1015 & \textbf{113,105} & \textbf{113,105} & \begin{tabular}[c]{@{}l@{}}IncFII(SARC14)\_1\_SARC14\_JQ418540;\\ IncFII(S)\_1\_\_CP000858\end{tabular} \\
 & \textbf{111,395} & \textbf{111,395} & - \\
 & \textbf{108,418} & 109,209$\vert$13 & IncFIB(K)\_1\_Kpn3\_JN233704 \\
 & \textbf{76,183} & \textbf{76,186} & IncL/M(pMU407)\_1\_pMU407\_U27345 \\
 & \textbf{11,638} & 11,892$\vert$2 & - \\ \hline
\end{tabular}
\end{adjustwidth}
\end{table}
